Bird beak's elaboration and innovation

### 2023-05-16 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

pdf(file = "../Manuscript/Figures/unscaled_ellipses.pdf", height = 8, width = 8)
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(colour.palette(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(colour.palette(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
covar.plot(order_shapespace,
           col = c(colour.palette(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(colour.palette(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
dev.off()
```

>>>>

pdf(file = "../Manuscript/Figures/unscaled_ellipses.pdf", height = 8, width = 8)
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(colour.palette(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(colour.palette(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
covar.plot(order_shapespace,
           col = c(colour.palette(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(colour.palette(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5, apply.to.VCV = TRUE)
dev.off()

pdf(file = "../Manuscript/Figures/50_random_axes_superorders.pdf", height = 8, width = 8)
load("../Data/Processed/tip_colours_super_orders.rda")
tip_colours_super_orders <- c(tip_colours_super_orders, "phylogeny" = "grey")
covar.plot(superorder_shapespace,
           transparent.scale = 1/3,
           n = 50,
           col = tip_colours_super_orders[name.subsets(superorder_shapespace)],
           main = "50 random scaled major axes per super order",
           major.axes = TRUE,
           legend = TRUE,
           points = FALSE,
           scale = "phylogeny",
           cex = 1)
dev.off()

```
